---
title: "xgboost"
output: html_document
---

```{r setup, include=FALSE}
require(xgboost)
#provides getTrainTest, convertToMatrix, and cleanDataSet
source('./src/data_prep.R')
source('./src/utils.R')
set.seed(50)
```

## Description

This document demonstrates the training and plots some charts around xgboost.  The goal of this model is to predict whether or not a shopper on Black Friday is male or female.  

```{r ingest}
cleanDataSet=loadData() %>% cleanData() %>% updateTarget("Gender")
summary(cleanDataSet)
```

## Data setup

```{r data}
#need the factor levels for when applying to new data
levels=getFactorLevels(cleanDataSet)
#xgboost requires pre-converted matrix
xgboostData=convertToMatrix(cleanDataSet, "Gender")
#test vs train
splitData=getTrainTest(xgboostData$features, xgboostData$target)
train=splitData$train
test=splitData$test
```

## Train Model

```{r model}
model=xgboost(data = train$features, label = train$target, max_depth = 4,
        eta = 1, nthread = 4, nrounds = 10,objective = "binary:logistic")
```

## Variable importance

The most important variables:

```{r importance, echo=FALSE}
plotImportance(model, colnames(train$features))
```


## Model performance

Confusion matrix at threshold 0.5:

```{r results}
getConfusionMatrixByThreshold=generateConfusionMatrixByThreshold(model, test$features, test$target)
getConfusionMatrixByThreshold(.5)
```

## Conclusion

The model performs slightly better than simply using the average male/female ratio in the test set.  We now save the model so we can load it and perform predictions:

```{r save}
save(model, file='./data/model.rdata')
save(levels, file='./data/levels.rdata')
```
